---
title: "PopDemog_figs"
author: "Brandie QC"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Code for Figures 2, 4, S9

## Load Libraries and other constants
```{r}
library(tidyverse)

BQDNDPalette <- c("#FF9900","#00CC00","#B266FF", "#999999", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

RILS_order <- c("Italy x Sweden","Germany x Tajikistan","UK x USA")

Dorm_order <- c("High", "Mixed", "Low")

Envt_order <- c('Control','High Humidity','Native Soil','Litter')
```

## Seedling Number - Figs 2a and S9A
```{r}
allyearstotalsdls <- read_csv("../Processed.Data/TotalSeedlings.csv")
```

### Control Treatment 
```{r}
allyearstotalsdls_summary_CTRL <- allyearstotalsdls %>% 
  mutate(Dormancy=str_replace(Dormancy, "Non-Dormant", "Low")) %>% 
  mutate(Dormancy=str_replace(Dormancy, "Dormant", "High")) %>% 
  filter(Envt=="Control") %>% 
  group_by(Year, Dormancy, RILSet) %>% 
  filter(!is.na(Totalsdls)) %>% 
  summarize(meanSdls=mean(Totalsdls), SE=sd(Totalsdls)/sqrt(n()))

allyearstotalsdls_summary_CTRL$Dormancy <- factor(allyearstotalsdls_summary_CTRL$Dormancy, levels = Dorm_order)

allyearstotalsdls_summary_CTRL %>% 
  ggplot(aes(x=Year, y=meanSdls, group=Dormancy, fill=Dormancy)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanSdls-SE,ymax=meanSdls+SE),
                width=.2, position = position_dodge(0.75)) +
  theme_classic() +
  xlab("Year") +
  ylab(paste0("Total Seedling Number")) +
  scale_fill_manual(values=BQDNDPalette) +
  theme(text=element_text(size=37),  panel.background = element_rect(fill = NA, color = "black")) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 200)) + 
  scale_x_discrete(limits=c("1", "2", "3")) +
  facet_grid(. ~factor(RILSet, level = RILS_order))
ggsave("../Figures/FigS9A_sdlnum_Ctrl.png", width=18, height=9, units="in")
```

### Italy x Sweden RIL Set
```{r}
allyearstotalsdls_summary_ENVT <- allyearstotalsdls %>% 
  mutate(Dormancy=str_replace(Dormancy, "Non-Dormant", "Low")) %>% 
  mutate(Dormancy=str_replace(Dormancy, "Dormant", "High")) %>% 
  filter(RILSet=="Italy x Sweden") %>% 
  group_by(Year, Dormancy, Envt) %>% 
  filter(!is.na(Totalsdls)) %>% 
  summarize(meanSdls=mean(Totalsdls), SE=sd(Totalsdls)/sqrt(n()))

allyearstotalsdls_summary_ENVT$Dormancy <- factor(allyearstotalsdls_summary_ENVT$Dormancy, levels = Dorm_order)
allyearstotalsdls_summary_ENVT$Envt <- factor(allyearstotalsdls_summary_ENVT$Envt, levels = Envt_order)

allyearstotalsdls_summary_ENVT %>% 
  ggplot(aes(x=Year, y=meanSdls, group=Dormancy, fill=Dormancy)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanSdls-SE,ymax=meanSdls+SE),
                width=.2, position = position_dodge(0.75)) +
  theme_classic() +
  xlab("Year") +
  ylab(paste0("Total Seedling Number")) +
  scale_fill_manual(values=BQDNDPalette) +
  theme(text=element_text(size=37),  panel.background = element_rect(fill = NA, color = "black")) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 350)) + 
  scale_x_discrete(limits=c("1", "2", "3")) +
  facet_grid(. ~Envt)
ggsave("../Figures/Fig2A_sdlnum_ENVT.png", width=18, height=9, units="in")
```

## Change in Seedling Number - Fig 4 and S9E
```{r}
sdls_flucts_long <- read_csv("../Processed.Data/SdlFlucts.csv")
```

### Control Treatment
```{r}
sdls_flucts_summary_CTRL <- sdls_flucts_long %>% 
  mutate(Dormancy=str_replace(Dormancy, "Non-Dormant", "Low")) %>% 
  mutate(Dormancy=str_replace(Dormancy, "Dormant", "High")) %>% 
  filter(Envt=="Control") %>% 
  group_by(Timepoint, Dormancy, RILSet) %>% 
  filter(!is.na(Fluct)) %>% 
  summarize(meanSdls=mean(Fluct), SE=sd(Fluct)/sqrt(n()))

sdls_flucts_summary_CTRL$Dormancy <- factor(sdls_flucts_summary_CTRL$Dormancy, levels = Dorm_order)

sdls_flucts_summary_CTRL %>% 
  ggplot(aes(x=Timepoint, y=meanSdls, group=Dormancy, fill=Dormancy)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanSdls-SE,ymax=meanSdls+SE),
                width=.2, position = position_dodge(0.75)) +
  theme_classic() +
  xlab("Time Period") +
  ylab(paste0("Change in Seedling #")) +
  scale_fill_manual(values=BQDNDPalette) +
  theme(text=element_text(size=37),  panel.background = element_rect(fill = NA, color = "black")) +
  facet_grid(. ~factor(RILSet, level = RILS_order))
ggsave("../Figures/FigS9E_sdlnumflucts_Ctrl.png", width=18, height=9, units="in")
```

### Italy x Swden RIL set
```{r}
sdls_flucts_summary_ENVT <- sdls_flucts_long %>% 
  mutate(Dormancy=str_replace(Dormancy, "Non-Dormant", "Low")) %>% 
  mutate(Dormancy=str_replace(Dormancy, "Dormant", "High")) %>% 
  filter(RILSet=="Italy x Sweden") %>% 
  group_by(Timepoint, Dormancy, Envt) %>% 
  filter(!is.na(Fluct)) %>% 
  summarize(meanSdls=mean(Fluct), SE=sd(Fluct)/sqrt(n()))

sdls_flucts_summary_ENVT$Dormancy <- factor(sdls_flucts_summary_ENVT$Dormancy, levels = Dorm_order)
sdls_flucts_summary_ENVT$Envt <- factor(sdls_flucts_summary_ENVT$Envt, levels = Envt_order)

sdls_flucts_summary_ENVT %>% 
  ggplot(aes(x=Timepoint, y=meanSdls, group=Dormancy, fill=Dormancy)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanSdls-SE,ymax=meanSdls+SE),
                width=.2, position = position_dodge(0.75)) +
  theme_classic() +
  xlab("Time Period") +
  ylab(paste0("Change in Seedling #")) +
  scale_fill_manual(values=BQDNDPalette) +
  theme(text=element_text(size=37),  panel.background = element_rect(fill = NA, color = "black")) +
  facet_grid(. ~Envt)
ggsave("../Figures/Fig4_sdlnumflucts_ENVT.png", width=18, height=9, units="in")
```

## Seedling Establishment - Fig 2b and S9B
```{r}
totseasonalsdlssurv <- read_csv("../Processed.Data/TOTALSeasonalSeedlingEstablishment.csv")
```

### Control Treatment
```{r}
totseasonalsdlssurv_summary_CTRL <- totseasonalsdlssurv %>% 
  mutate(Dormancy=str_replace(Dormancy, "Non-Dormant", "Low")) %>% 
  mutate(Dormancy=str_replace(Dormancy, "Dormant", "High")) %>% 
  filter(Envt=="Control") %>% 
  group_by(Season, Dormancy, RILSet) %>% 
  filter(!is.na(seasonalEst)) %>% 
  summarize(meanSurv=mean(seasonalEst), SE=sd(seasonalEst)/sqrt(n()))

totseasonalsdlssurv_summary_CTRL$Season <- factor(totseasonalsdlssurv_summary_CTRL$Season, levels = c('1_Summer','1_Autumn','2_Summer','2_Autumn'))
totseasonalsdlssurv_summary_CTRL$Dormancy <- factor(totseasonalsdlssurv_summary_CTRL$Dormancy, levels = Dorm_order)

seasonalsurv_ctrl_plot <- totseasonalsdlssurv_summary_CTRL %>% ggplot(aes(x=Season, y=meanSurv, group=Dormancy, fill=Dormancy)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanSurv-SE,ymax=meanSurv+SE),width=.2, position = 
                  position_dodge(0.75)) +
  theme_classic() +
  xlab("Year_Season") +
  ylab(paste0("Proportion of Seedling Establishment")) +
  scale_fill_manual(values=BQDNDPalette) +
  theme(text=element_text(size=30), panel.background = element_rect(fill = NA, color = "black"), axis.text.x = element_text(angle = 45,  hjust = 1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(-0.005, 1)) +
  facet_grid(factor(RILSet, level = RILS_order) ~.)
ggsave("../Figures/FigS9B_seasonalSdlEst_Ctrl.png", width=16, height=12, units="in")
```

### Italy x Swden RIL set
```{r}
totseasonalsdlssurv_summary_IS <- totseasonalsdlssurv %>% 
  mutate(Dormancy=str_replace(Dormancy, "Non-Dormant", "Low")) %>% 
  mutate(Dormancy=str_replace(Dormancy, "Dormant", "High")) %>% 
  filter(RILSet=="Italy x Sweden") %>% 
  group_by(Season, Dormancy, Envt) %>% 
  filter(!is.na(seasonalEst)) %>% 
  summarize(meanSurv=mean(seasonalEst), SE=sd(seasonalEst)/sqrt(n()))

totseasonalsdlssurv_summary_IS$Envt <- factor(totseasonalsdlssurv_summary_IS$Envt, levels = Envt_order)
totseasonalsdlssurv_summary_IS$Season <- factor(totseasonalsdlssurv_summary_IS$Season, levels = c('1_Summer','1_Autumn','2_Summer','2_Autumn'))
totseasonalsdlssurv_summary_IS$Dormancy <- factor(totseasonalsdlssurv_summary_IS$Dormancy, levels = Dorm_order)

seasonalsurv_IS_plot <- totseasonalsdlssurv_summary_IS %>% 
  ggplot(aes(x=Season, y=meanSurv, group=Dormancy, fill=Dormancy)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanSurv-SE,ymax=meanSurv+SE),width=.2, position = position_dodge(0.75)) +
  theme_classic() +
  xlab("Year_Season") +
  ylab(paste0("Proportion of Seedling Establishment")) +
  scale_fill_manual(values=BQDNDPalette) +
  theme(text=element_text(size=30), panel.background = element_rect(fill = NA, color = "black"), axis.text.x = element_text(angle = 45,  hjust = 1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(-0.005, 1)) +
  facet_grid(Envt ~.)
ggsave("../Figures/Fig2B_seasonalSdlEst_Envt.png", width=16, height=12, units="in")
```

## Survival to Rosette from Seedling - Fig 2c and S9C
```{r}
sdltorosettesurv_calc <- read_csv("../Processed.Data/SurvtoRose.csv")
```

### Control Treatment
```{r}
survtorose_1_CTRL_summary <- sdltorosettesurv_calc %>% 
  mutate(Dormancy=str_replace(Dormancy, "Non-Dormant", "Low")) %>% 
  mutate(Dormancy=str_replace(Dormancy, "Dormant", "High")) %>% 
  filter(Envt=="Control") %>% 
  filter(Year != 3)%>%
  group_by(Year, Dormancy, RILSet) %>% 
  filter(!is.na(SurvtoRose)) %>% 
  summarize(meanSurv=mean(SurvtoRose), SE=sd(SurvtoRose)/sqrt(n()))

survtorose_1_CTRL_summary$Dormancy <- factor(survtorose_1_CTRL_summary$Dormancy, levels = Dorm_order)

survtorose_1_CTRL_summary %>% 
    ggplot(aes(x=Year, y=meanSurv, group=Dormancy, fill=Dormancy)) +
    geom_col(width = 0.7,position = position_dodge(0.75)) +
     geom_errorbar(aes(ymin=meanSurv-SE,ymax=meanSurv+SE),width=.2, position = 
                    position_dodge(0.75)) +
    theme_classic() +
    xlab("Year") +
    ylab("Survival to Rosette") +
    scale_fill_manual(values=BQDNDPalette) +
    theme(text=element_text(size=37), panel.background = element_rect(fill = NA, color = "black")) +
    scale_y_continuous(expand = expansion(mult = c(0, 0)), limits = c(-0.001, 1)) +
    scale_x_continuous(breaks = seq(1, 3, by = 1)) +
    facet_grid(. ~factor(RILSet, level = RILS_order))
ggsave("../Figures/FigS9C_SurvtoRose_Ctrl.png", width=18, height=9, units="in")
```

### Italy x Swden RIL set
```{r}
survtorose_1_IS_summary <- sdltorosettesurv_calc %>% 
  mutate(Dormancy=str_replace(Dormancy, "Non-Dormant", "Low")) %>% 
  mutate(Dormancy=str_replace(Dormancy, "Dormant", "High")) %>% 
  filter(RILSet=="Italy x Sweden") %>% 
  filter(Year != 3)%>%
  group_by(Year, Dormancy, Envt) %>% 
  filter(!is.na(SurvtoRose)) %>% 
  summarize(meanSurv=mean(SurvtoRose), SE=sd(SurvtoRose)/sqrt(n()))

survtorose_1_IS_summary$Dormancy <- factor(survtorose_1_IS_summary$Dormancy, levels = Dorm_order)
survtorose_1_IS_summary$Envt <- factor(survtorose_1_IS_summary$Envt, levels = Envt_order)

survtorose_1_IS_summary %>% 
    ggplot(aes(x=Year, y=meanSurv, group=Dormancy, fill=Dormancy)) +
    geom_col(width = 0.7,position = position_dodge(0.75)) +
     geom_errorbar(aes(ymin=meanSurv-SE,ymax=meanSurv+SE),width=.2, position = 
                    position_dodge(0.75)) +
    theme_classic() +
    xlab("Year") +
    ylab("Survival to Rosette") +
    scale_fill_manual(values=BQDNDPalette) +
    theme(text=element_text(size=37), panel.background = element_rect(fill = NA, color = "black")) +
    scale_y_continuous(expand = expansion(mult = c(0, 0)), limits = c(-0.001, 1)) +
    scale_x_continuous(breaks = seq(1, 3, by = 1)) +
    facet_grid(. ~Envt)
ggsave("../Figures/Fig2C_SurvtoRose_ENVT.png", width=18, height=9, units="in")
```

## Survival to Reproduction from Rosette - Fig 2D and S9D
```{r}
survtoFRMD_circle_calc <- read_csv("../Processed.Data/RoseSurvtoFRMD.csv")
```

### Control Treatment
```{r}
df_frmd_ctrl <- tibble(Year=c(2,2), Dormancy=c("High", "Low"), RILSet=c("UK x USA", "UK x USA"), meanSurv=0, SE=0)

survtoFRMD_CTRL_summary <- survtoFRMD_circle_calc %>% 
  mutate(Dormancy=str_replace(Dormancy, "Non-Dormant", "Low")) %>% 
  mutate(Dormancy=str_replace(Dormancy, "Dormant", "High")) %>% 
  filter(Envt=="Control") %>% 
  group_by(Year, Dormancy, RILSet) %>% 
  filter(!is.na(RoseSurv)) %>% 
  summarize(meanSurv=mean(RoseSurv), SE=sd(RoseSurv)/sqrt(n())) %>% 
  bind_rows(df_frmd_ctrl)

survtoFRMD_CTRL_summary$Dormancy <- factor(survtoFRMD_CTRL_summary$Dormancy, levels = Dorm_order)

survtoFRMD_CTRL_summary %>% 
    ggplot(aes(x=Year, y=meanSurv, group=Dormancy, fill=Dormancy)) +
    geom_col(width = 0.7,position = position_dodge(0.75)) +
     geom_errorbar(aes(ymin=meanSurv-SE,ymax=meanSurv+SE),width=.2, position = 
                    position_dodge(0.75)) +
    theme_classic() +
    xlab("Year") +
    ylab("Rosette to Reproductive Survival") +
    scale_fill_manual(values=BQDNDPalette) +
    scale_x_continuous(breaks = seq(1, 3, by = 1)) +
   theme(text=element_text(size=37), panel.background = element_rect(fill = NA, color = "black")) +
  scale_y_continuous(expand = expansion(mult = c(0.001,0)), limits = c(0, 1)) +
   facet_grid(. ~factor(RILSet, level = RILS_order))
ggsave("../Figures/FigS9D_SurvtoFRMD_CTRL.png", width=18, height=9, units="in")
```

### Italy x Swden RIL set
```{r}
survtoFRMD_ENVT_summary <- survtoFRMD_circle_calc %>% 
  mutate(Dormancy=str_replace(Dormancy, "Non-Dormant", "Low")) %>% 
  mutate(Dormancy=str_replace(Dormancy, "Dormant", "High")) %>% 
  filter(RILSet=="Italy x Sweden") %>% 
  group_by(Year, Dormancy, Envt) %>% 
  filter(!is.na(RoseSurv)) %>% 
  summarize(meanSurv=mean(RoseSurv), SE=sd(RoseSurv)/sqrt(n()))

survtoFRMD_ENVT_summary$Dormancy <- factor(survtoFRMD_ENVT_summary$Dormancy, levels = Dorm_order)
survtoFRMD_ENVT_summary$Envt <- factor(survtoFRMD_ENVT_summary$Envt, levels = Envt_order)

survtoFRMD_ENVT_summary %>% 
  ggplot(aes(x=Year, y=meanSurv, group=Dormancy, fill=Dormancy)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanSurv-SE,ymax=meanSurv+SE),
                width=.2, position = position_dodge(0.75)) +
  theme_classic() +
  xlab("Year") +
  ylab("Rosette to Reproductive Survival") +
  scale_fill_manual(values=BQDNDPalette) +
  scale_x_continuous(breaks = seq(1, 3, by = 1)) +
  theme(text=element_text(size=37), panel.background = element_rect(fill = NA, color = "black")) +
  scale_y_continuous(expand = expansion(mult = c(0, .2)), limits = c(0, 1)) +
  facet_grid(. ~Envt)
ggsave("../Figures/Fig2D_SurvtoFRMD_ENVT.png", width=18, height=9, units="in")
```
