---
title: "PopPers_figs"
author: "Brandie QC"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Code for making population persistence figures (Figures 5 and S9F)

## Load libraries and constants
```{r}
library(tidyverse)

level_order_y1 <- c("Never Established", "Established then Disappeared", "Established and Persisted")
level_order_y2 <- c("Disappeared after Year 1", "Newly Established then Disappeared", "Reappeared then Disappeared", "Persisted then Disappeared", "Persisted")
level_order_y3 <- c("Disappeared", "Reappeared", "Persisted")
```

## Load Pop Persistence Data
```{r}
poppers <- read_csv("../Processed.Data/PopPersistence.csv")
```

## Year 1 
```{r}
BSy1 <- poppers %>% 
  select(PopId:Envt, Y1Persistence) %>% 
  filter(RILSet=="Germany x Tajikistan", Envt=="Control")

TCy1 <- poppers %>% 
  select(PopId:Envt, Y1Persistence) %>% 
  filter(RILSet=="UK x USA")

ISy1 <- poppers %>% 
  select(PopId:Envt, Y1Persistence) %>% 
  filter(RILSet=="Italy x Sweden", Envt=="Control")

y1humid <- poppers %>% 
  select(PopId:Envt, Y1Persistence) %>% 
  filter(RILSet=="Italy x Sweden", Envt=="High Humidity")

y1soil <- poppers %>% 
  select(PopId:Envt, Y1Persistence) %>% 
  filter(RILSet=="Italy x Sweden", Envt=="Native Soil")

y1straw <- poppers %>% 
  select(PopId:Envt, Y1Persistence) %>% 
  filter(RILSet=="Italy x Sweden", Envt=="Straw Litter" )
```

### Germany x Tajikistan
```{r}
#First, make a contingency table from the data 
BSy1_contingtable <- table(BSy1$Dormancy, BSy1$Y1Persistence)

#make a graph - convert to long format 
BSy1prop <- prop.table(BSy1_contingtable, 1) #proportions 

BSdfpers <- as.data.frame.matrix(BSy1prop)
BSdfpers$DORM <- c("Dormant", "Mixed", "Non-Dormant")
BSdfpers$RIL <-c("Germany x Tajikistan", "Germany x Tajikistan", "Germany x Tajikistan")

#Perform a chi-square test 
BSy1chisq <- chisq.test(BSy1_contingtable)

BSdfpers_long <- gather(BSdfpers, Status, Proportion, "Established and Persisted":"Never Established", factor_key=TRUE)
  
BSy1persgraph <- BSdfpers_long %>% ggplot(aes(y=Proportion, x=DORM, fill=factor(Status, level=level_order_y1))) + 
    geom_bar(stat="identity", position = "fill", alpha=0.9) + 
    theme_classic() + 
    #labs(y=paste0("Prop. of","\n", "Populations"), x="Dormancy") + 
    theme(text=element_text(size=30), legend.position = "none", 
          axis.title.y=element_blank(), axis.text.y=element_blank(),
          axis.title.x=element_blank(), axis.text.x=element_blank()) +
    scale_x_discrete(expand = expansion(mult = c(0,0))) + 
    scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, 1)) + 
    scale_fill_manual(values=c("#000000", "#E69F00", "#009E73"))
ggsave("../Figures/PopPersistence/FigS9F_PopPers_GermTaj_Y1.png", width=10, height=5, units="in")
```

### UK x USA
```{r}
#First, make a contingency table from the data
TCy1_contingtable <- table(TCy1$Dormancy, TCy1$Y1Persistence)
  
#Perform a chi-square test 
TCy1chisq <- chisq.test(TCy1_contingtable)

#make a graph - convert to long format 
TCy1prop <- prop.table(TCy1_contingtable, 1) #proportions 
  
TCdfpers <- as.data.frame.matrix(TCy1prop)
TCdfpers$DORM <- c("Dormant", "Mixed", "Non-Dormant")
TCdfpers$RIL <-c("UK x USA", "UK x USA", "UK x USA")

TCdfpers_long <- gather(TCdfpers, Status, Proportion, "Established and Persisted":"Never Established", factor_key=TRUE)

TCy1persgraph <- TCdfpers_long %>% ggplot(aes(y=Proportion, x=DORM, fill=factor(Status, level=level_order_y1))) + 
    geom_bar(stat="identity", position = "fill", alpha=0.9) + 
    theme_classic() + 
    #labs(y=paste0("Prop. of","\n", "Populations"), x="Dormancy") + 
    theme(text=element_text(size=30), legend.position = "none", 
          axis.title.y=element_blank(), axis.text.y=element_blank(),
          axis.title.x=element_blank(), axis.text.x=element_blank()) +
    scale_x_discrete(expand = expansion(mult = c(0,0))) + 
    scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, 1)) + 
    scale_fill_manual(values=c("#000000", "#E69F00", "#009E73"))
ggsave("../Figures/PopPersistence/FigS9F_PopPers_UKUSA_Y1.png", width=10, height=5, units="in")
```

### Italy x Sweden Control
```{r}
#First, make a contingency table from the data
ISy1_contingtable <- table(ISy1$Dormancy, ISy1$Y1Persistence)

#Perform a chi-square test 
ISy1chisq <- chisq.test(ISy1_contingtable)

#make a graph - convert to long format 
ISy1prop <- prop.table(ISy1_contingtable, 1) #proportions 

ISdfpers <- as.data.frame.matrix(ISy1prop)
ISdfpers$DORM <- c("Dormant", "Mixed", "Non-Dormant")
ISdfpers$RIL <-c("Italy x Sweden", "Italy x Sweden", "Italy x Sweden")

ISdfpers_long <- gather(ISdfpers, Status, Proportion, "Established and Persisted":"Never Established", factor_key=TRUE)
  
ISy1persgraph <- ISdfpers_long %>% ggplot(aes(y=Proportion, x=DORM, fill=factor(Status, level=level_order_y1))) + 
    geom_bar(stat="identity", position = "fill", alpha=0.9) + 
    theme_classic() + 
    #labs(y=paste0("Prop. of","\n", "Populations"), x="Dormancy") + 
    theme(text=element_text(size=30), legend.position = "none", 
          axis.title.y=element_blank(), axis.text.y=element_blank(),
          axis.title.x=element_blank(), axis.text.x=element_blank()) +
    scale_x_discrete(expand = expansion(mult = c(0,0))) + 
    scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, 1)) +
    scale_fill_manual(values=c("#000000", "#E69F00", "#009E73"))
ggsave("../Figures/PopPersistence/Fig5_PopPers_ISCtrl_Y1.png", width=10, height=5, units="in")
```

### Italy x Sweden HH
```{r}
#First, make a contingency table from the data
y1humid_contingtable <- table(y1humid$Dormancy, y1humid$Y1Persistence)

#Perform a chi-square test 
y1humidchisq <- chisq.test(y1humid_contingtable)

#make a graph - convert to long format 
y1humidprop <- prop.table(y1humid_contingtable, 1) #proportions 

humiddfpers <- as.data.frame.matrix(y1humidprop)
humiddfpers$DORM <- c("Dormant", "Mixed", "Non-Dormant")
humiddfpers$RIL <-c("High Humidity","High Humidity","High Humidity")

humiddfpers_long <- gather(humiddfpers, Status, Proportion, "Established and Persisted":"Established then Disappeared", factor_key=TRUE)

humidy1persgraph <- humiddfpers_long %>% ggplot(aes(y=Proportion, x=DORM, fill=factor(Status, level=level_order_y1))) + 
    geom_bar(stat="identity", position = "fill", alpha=0.9) + 
    theme_classic() + 
    theme(text=element_text(size=30), legend.position = "none",            axis.title.y=element_blank(), axis.text.y=element_blank(),           axis.title.x=element_blank(), axis.text.x=element_blank()) +     scale_x_discrete(expand = expansion(mult = c(0,0))) +      scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, 1)) +
    scale_fill_manual(values=c("#E69F00", "#009E73"))
ggsave("../Figures/PopPersistence/Fig5_PopPers_ISHH_Y1.png", width=10, height=5, units="in")
```

### Italy x Sweden Native Soil
```{r}
#First, make a contingency table from the data
y1soil_contingtable <- table(y1soil$Dormancy, y1soil$Y1Persistence)

#Perform a chi-square test 
y1soilchisq <- chisq.test(y1soil_contingtable)

#make a graph - convert to long format 
y1soilprop <- prop.table(y1soil_contingtable, 1) #proportions 

soildfpers <- as.data.frame.matrix(y1soilprop)
soildfpers$DORM <- c("Dormant", "Mixed", "Non-Dormant")
soildfpers$RIL <-c("Drought","Drought","Drought")

soildfpers_long <- gather(soildfpers, Status, Proportion, "Established and Persisted", factor_key=TRUE)
  
soily1persgraph <- soildfpers_long %>% ggplot(aes(y=Proportion, x=DORM, fill=factor(Status, level=level_order_y1))) + 
    geom_bar(stat="identity", position = "fill", alpha=0.9) + 
    theme_classic() + 
    theme(text=element_text(size=30), legend.position = "none",            axis.title.y=element_blank(), axis.text.y=element_blank(),           axis.title.x=element_blank(), axis.text.x=element_blank()) +     scale_x_discrete(expand = expansion(mult = c(0,0))) +      scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, 1)) +
    scale_fill_manual(values=c("#009E73"))
ggsave("../Figures/PopPersistence/Fig5_PopPers_ISNS_Y1.png", width=10, height=5, units="in")
```

### Italy x Sweden Litter
```{r}
#First, make a contingency table from the data
y1straw_contingtable <- table(y1straw$Dormancy, y1straw$Y1Persistence)

#Perform a chi-square test 
y1strawchisq <- chisq.test(y1straw_contingtable)

#make a graph - convert to long format 
y1strawprop <- prop.table(y1straw_contingtable, 1) #proportions 

strawdfpers <- as.data.frame.matrix(y1strawprop)
strawdfpers$DORM <- c("Dormant", "Mixed", "Non-Dormant")
strawdfpers$RIL <-c("Drought","Drought","Drought")

strawdfpers_long <- gather(strawdfpers, Status, Proportion, "Established and Persisted":"Never Established", factor_key=TRUE)
  
strawy1persgraph <- strawdfpers_long %>% ggplot(aes(y=Proportion, x=DORM, fill=factor(Status, level=level_order_y1))) + 
    geom_bar(stat="identity", position = "fill", alpha=0.9) + 
    theme_classic() + 
    theme(text=element_text(size=30), legend.position = "none",            axis.title.y=element_blank(), axis.text.y=element_blank(),           axis.title.x=element_blank(), axis.text.x=element_blank()) +     scale_x_discrete(expand = expansion(mult = c(0,0))) +      scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, 1)) +
    scale_fill_manual(values=c("#000000", "#E69F00", "#009E73"))
ggsave("../Figures/PopPersistence/Fig5_PopPers_ISLitter_Y1.png", width=10, height=5, units="in")
```

## Year 2
```{r}
BSy2 <- poppers %>% 
  select(PopId:Envt, Y2Persistence) %>% 
  filter(RILSet=="Germany x Tajikistan", Envt=="Control")

TCy2 <- poppers %>% 
  select(PopId:Envt, Y2Persistence) %>% 
  filter(RILSet=="UK x USA")

ISy2 <- poppers %>% 
  select(PopId:Envt, Y2Persistence) %>% 
  filter(RILSet=="Italy x Sweden", Envt=="Control")

y2humid <- poppers %>% 
  select(PopId:Envt, Y2Persistence) %>% 
  filter(RILSet=="Italy x Sweden", Envt=="High Humidity")

y2soil <- poppers %>% 
  select(PopId:Envt, Y2Persistence) %>% 
  filter(RILSet=="Italy x Sweden", Envt=="Native Soil")

y2straw <- poppers %>% 
  select(PopId:Envt, Y2Persistence) %>% 
  filter(RILSet=="Italy x Sweden", Envt=="Straw Litter" )
```

### Germany x Tajikistan
```{r}
#First, make a contingency table from the data
BSy2_contingtable <- table(BSy2$Dormancy, BSy2$Y2Persistence)
  
#Perform a chi-square test 
BSy2chisq <- chisq.test(BSy2_contingtable)

#make a graph - convert to long format 
BSy2prop <- prop.table(BSy2_contingtable, 1) #proportions 

BSdfpers <- as.data.frame.matrix(BSy2prop)
BSdfpers$DORM <- c("Dormant", "Mixed", "Non-Dormant")
BSdfpers$RIL <-c("Germany x Tajikistan", "Germany x Tajikistan", "Germany x Tajikistan")
BSdfpers_long <- gather(BSdfpers, Status, Proportion, "Disappeared after Year 1":"Reappeared then Disappeared", factor_key=TRUE)
  
BSy1persgraph <- BSdfpers_long %>% ggplot(aes(y=Proportion, x=DORM, fill=factor(Status, level=level_order_y2))) + 
    geom_bar(stat="identity", position = "fill", alpha=0.9) + 
    theme_classic() + 
    theme(text=element_text(size=30), legend.position = "none",            axis.title.y=element_blank(), axis.text.y=element_blank(),           axis.title.x=element_blank(), axis.text.x=element_blank()) +     scale_x_discrete(expand = expansion(mult = c(0,0))) +      scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, 1)) +
    scale_fill_manual(values=c("#FFFF99","#994C00", "#E69F00","#D55E00","#009E73"))
ggsave("../Figures/PopPersistence/FigS9F_PopPers_GermTaj_Y2.png", width=10, height=5, units="in")
```

### UK x USA
```{r}
#First, make a contingency table from the data
TCy2_contingtable <- table(TCy2$Dormancy, TCy2$Y2Persistence)

#Perform a chi-square test 
TCy2chisq <- chisq.test(TCy2_contingtable)

#make a graph - convert to long format 
TCy2prop <- prop.table(TCy2_contingtable, 1) #proportions 

TCdfpers <- as.data.frame.matrix(TCy2prop)
TCdfpers$DORM <- c("Dormant", "Mixed", "Non-Dormant")
TCdfpers$RIL <-c("UK x USA", "UK x USA", "UK x USA")

TCdfpers_long <- gather(TCdfpers, Status, Proportion, "Disappeared after Year 1":"Reappeared then Disappeared", factor_key=TRUE)
  
TCy1persgraph <- TCdfpers_long %>% ggplot(aes(y=Proportion, x=DORM, fill=factor(Status, level=level_order_y2))) + 
    geom_bar(stat="identity", position = "fill", alpha=0.9) + 
    theme_classic() + 
    theme(text=element_text(size=30), legend.position = "none",            axis.title.y=element_blank(), axis.text.y=element_blank(),           axis.title.x=element_blank(), axis.text.x=element_blank()) +     scale_x_discrete(expand = expansion(mult = c(0,0))) +      scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, 1)) +
    scale_fill_manual(values=c("#FFFF99","#994C00", "#E69F00","#D55E00","#009E73"))
ggsave("../Figures/PopPersistence/FigS9F_PopPers_UKUSA_Y2.png", width=10, height=5, units="in")
```

### Italy x Sweden Control
```{r}
#First, make a contingency table from the data
ISy2_contingtable <- table(ISy2$Dormancy, ISy2$Y2Persistence)

#Perform a chi-square test 
ISy2chisq <- chisq.test(ISy2_contingtable)

#make a graph - convert to long format 
ISy2prop <- prop.table(ISy2_contingtable, 1) #proportions 

ISdfpers <- as.data.frame.matrix(ISy2prop)
ISdfpers$DORM <- c("Dormant", "Mixed", "Non-Dormant")
ISdfpers$RIL <-c("Italy x Sweden", "Italy x Sweden", "Italy x Sweden")

ISdfpers_long <- gather(ISdfpers, Status, Proportion, "Disappeared after Year 1":"Reappeared then Disappeared", factor_key=TRUE)
  
ISy1persgraph <- ISdfpers_long %>% ggplot(aes(y=Proportion, x=DORM, fill=factor(Status, level=level_order_y2))) + 
    geom_bar(stat="identity", position = "fill", alpha=0.9) + 
    theme_classic() + 
    theme(text=element_text(size=30), legend.position = "none",            axis.title.y=element_blank(), axis.text.y=element_blank(),           axis.title.x=element_blank(), axis.text.x=element_blank()) +     scale_x_discrete(expand = expansion(mult = c(0,0))) +      scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, 1)) +
    scale_fill_manual(values=c("#FFFF99","#994C00", "#E69F00","#D55E00","#009E73"))
ggsave("../Figures/PopPersistence/Fig5_PopPers_ISCtrl_Y2.png", width=10, height=5, units="in")
```

### Italy x Sweden HH
```{r}
#First, make a contingency table from the data
y2humid_contingtable <- table(y2humid$Dormancy, y2humid$Y2Persistence)

#Perform a chi-square test 
y2humidchisq <- chisq.test(y2humid_contingtable)

#make a graph - convert to long format 
y2humidprop <- prop.table(y2humid_contingtable, 1) #proportions 

humiddfpers <- as.data.frame.matrix(y2humidprop)
humiddfpers$DORM <- c("Dormant", "Mixed", "Non-Dormant")
humiddfpers$RIL <-c("Drought","Drought","Drought")
humiddfpers_long <- gather(humiddfpers, Status, Proportion, "Disappeared after Year 1":"Reappeared then Disappeared", factor_key=TRUE)
  
humidy1persgraph <- humiddfpers_long %>% ggplot(aes(y=Proportion, x=DORM, fill=factor(Status, level=level_order_y2))) + 
    geom_bar(stat="identity", position = "fill", alpha=0.9) + 
    theme_classic() + 
    theme(text=element_text(size=30), legend.position = "none",            axis.title.y=element_blank(), axis.text.y=element_blank(),           axis.title.x=element_blank(), axis.text.x=element_blank()) +     scale_x_discrete(expand = expansion(mult = c(0,0))) +      scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, 1)) +
    scale_fill_manual(values=c("#FFFF99", "#E69F00","#D55E00","#009E73"))
ggsave("../Figures/PopPersistence/Fig5_PopPers_ISHH_Y2.png", width=10, height=5, units="in")
```

### Italy x Sweden Native Soil
```{r}
#First, make a contingency table from the data
y2soil_contingtable <- table(y2soil$Dormancy, y2soil$Y2Persistence)

#Perform a chi-square test 
y2soilchisq <- chisq.test(y2soil_contingtable)

#make a graph - convert to long format 
y2soilprop <- prop.table(y2soil_contingtable, 1) #proportions 

soildfpers <- as.data.frame.matrix(y2soilprop)
soildfpers$DORM <- c("Dormant", "Mixed", "Non-Dormant")
soildfpers$RIL <-c("Drought","Drought","Drought")
soildfpers_long <- gather(soildfpers, Status, Proportion, "Disappeared after Year 1":"Persisted then Disappeared", factor_key=TRUE)
  
soily1persgraph <- soildfpers_long %>% ggplot(aes(y=Proportion, x=DORM, fill=factor(Status, level=level_order_y2))) + 
    geom_bar(stat="identity", position = "fill", alpha=0.9) + 
    theme_classic() + 
    theme(text=element_text(size=30), legend.position = "none",            axis.title.y=element_blank(), axis.text.y=element_blank(),           axis.title.x=element_blank(), axis.text.x=element_blank()) +     scale_x_discrete(expand = expansion(mult = c(0,0))) +      scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, 1)) +
    scale_fill_manual(values=c("#FFFF99","#D55E00","#009E73"))
ggsave("../Figures/PopPersistence/Fig5_PopPers_ISNS_Y2.png", width=10, height=5, units="in")
```

### Italy x Sweden Litter
```{r}
#First, make a contingency table from the data
y2straw_contingtable <- table(y2straw$Dormancy, y2straw$Y2Persistence)

#Perform a chi-square test 
y2strawchisq <- chisq.test(y2straw_contingtable)

#make a graph - convert to long format 
y2strawprop <- prop.table(y2straw_contingtable, 1) #proportions 

strawdfpers <- as.data.frame.matrix(y2strawprop)
strawdfpers$DORM <- c("Dormant", "Mixed", "Non-Dormant")
strawdfpers$RIL <-c("Drought","Drought","Drought")
strawdfpers_long <- gather(strawdfpers, Status, Proportion, "Disappeared after Year 1":"Reappeared then Disappeared", factor_key=TRUE)
  
strawy1persgraph <- strawdfpers_long %>% ggplot(aes(y=Proportion, x=DORM, fill=factor(Status, level=level_order_y2))) + 
    geom_bar(stat="identity", position = "fill", alpha=0.9) + 
    theme_classic() + 
    theme(text=element_text(size=30), legend.position = "none",            axis.title.y=element_blank(), axis.text.y=element_blank(),           axis.title.x=element_blank(), axis.text.x=element_blank()) +     scale_x_discrete(expand = expansion(mult = c(0,0))) +      scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, 1)) +
    scale_fill_manual(values=c("#FFFF99","#994C00", "#E69F00","#D55E00","#009E73"))
ggsave("../Figures/PopPersistence/Fig5_PopPers_ISLitter_Y2.png", width=10, height=5, units="in")
```

## Year 3
```{r}
BSy3 <- poppers %>% 
  select(PopId:Envt, Y3Resurrection) %>% 
  filter(RILSet=="Germany x Tajikistan", Envt=="Control")

TCy3 <- poppers %>% 
  select(PopId:Envt, Y3Resurrection) %>% 
  filter(RILSet=="UK x USA")

ISy3 <- poppers %>% 
  select(PopId:Envt, Y3Resurrection) %>% 
  filter(RILSet=="Italy x Sweden", Envt=="Control")

y3humid <- poppers %>% 
  select(PopId:Envt, Y3Resurrection) %>% 
  filter(RILSet=="Italy x Sweden", Envt=="High Humidity")

y3soil <- poppers %>% 
  select(PopId:Envt, Y3Resurrection) %>% 
  filter(RILSet=="Italy x Sweden", Envt=="Native Soil")

y3straw <- poppers %>% 
  select(PopId:Envt, Y3Resurrection) %>% 
  filter(RILSet=="Italy x Sweden", Envt=="Straw Litter" )
```

### Germany x Tajikistan
```{r}
#First, make a contingency table from the data
BSy3_contingtable <- table(BSy3$Dormancy, BSy3$Y3Resurrection)

#Perform a chi-square test 
BSy3chisq <- chisq.test(BSy3_contingtable)

#make a graph - convert to long format 
BSy3prop <- prop.table(BSy3_contingtable, 1) #proportions 

BSdfpers <- as.data.frame.matrix(BSy3prop)
BSdfpers$DORM <- c("Dormant", "Mixed", "Non-Dormant")
BSdfpers$RIL <-c("Germany x Tajikistan", "Germany x Tajikistan", "Germany x Tajikistan")
BSdfpers_long <- gather(BSdfpers, Status, Proportion, "Disappeared":"Reappeared", factor_key=TRUE)
  
BSy1persgraph <- BSdfpers_long %>% ggplot(aes(y=Proportion, x=DORM, fill=factor(Status, level=level_order_y3))) +  
    geom_bar(stat="identity", position = "fill", alpha=0.9) + 
    theme_classic() + 
    theme(text=element_text(size=30), legend.position = "none",            axis.title.y=element_blank(), axis.text.y=element_blank(),           axis.title.x=element_blank(), axis.text.x=element_blank()) +     scale_x_discrete(expand = expansion(mult = c(0,0))) +      scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, 1)) +
    scale_fill_manual(values=c("#FFFF99","#00CCCC","#009E73"))
ggsave("../Figures/PopPersistence/FigS9F_PopPers_GermTaj_Y3.png", width=10, height=5, units="in")
```

### UK x USA
```{r}
#First, make a contingency table from the data
TCy3_contingtable <- table(TCy3$Dormancy, TCy3$Y3Resurrection)

#Perform a chi-square test 
TCy3chisq <- chisq.test(TCy3_contingtable)

#make a graph - convert to long format 
TCy3prop <- prop.table(TCy3_contingtable, 1) #proportions 

TCdfpers <- as.data.frame.matrix(TCy3prop)
TCdfpers$DORM <- c("Dormant", "Mixed", "Non-Dormant")
TCdfpers$RIL <-c("UK x USA", "UK x USA", "UK x USA")
TCdfpers_long <- gather(TCdfpers, Status, Proportion, "Persisted":"Reappeared", factor_key=TRUE)
  
TCy1persgraph <- TCdfpers_long %>% ggplot(aes(y=Proportion, x=DORM, fill=factor(Status, level=level_order_y3))) + 
    geom_bar(stat="identity", position = "fill", alpha=0.9) + 
    theme_classic() + 
    theme(text=element_text(size=30), legend.position = "none",            axis.title.y=element_blank(), axis.text.y=element_blank(),           axis.title.x=element_blank(), axis.text.x=element_blank()) +     scale_x_discrete(expand = expansion(mult = c(0,0))) +      scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, 1)) +
    scale_fill_manual(values=c("#00CCCC","#009E73"))
ggsave("../Figures/PopPersistence/FigS9F_PopPers_UKUSA_Y3.png", width=10, height=5, units="in")
```

### Italy x Sweden Control
```{r}
#First, make a contingency table from the data
ISy3_contingtable <- table(ISy3$Dormancy, ISy3$Y3Resurrection)

#Perform a chi-square test 
ISy3chisq <- chisq.test(ISy3_contingtable)

#make a graph - convert to long format 
ISy3prop <- prop.table(ISy3_contingtable, 1) #proportions 

ISdfpers <- as.data.frame.matrix(ISy3prop)
ISdfpers$DORM <- c("Dormant", "Mixed", "Non-Dormant")
ISdfpers$RIL <-c("Italy x Sweden", "Italy x Sweden", "Italy x Sweden")
ISdfpers_long <- gather(ISdfpers, Status, Proportion, "Persisted":"Reappeared", factor_key=TRUE)
  
ISy1persgraph <- ISdfpers_long %>% ggplot(aes(y=Proportion, x=DORM, fill=factor(Status, level=level_order_y3))) +  
    geom_bar(stat="identity", position = "fill", alpha=0.9) + 
    theme_classic() + 
    theme(text=element_text(size=30), legend.position = "none",            axis.title.y=element_blank(), axis.text.y=element_blank(),           axis.title.x=element_blank(), axis.text.x=element_blank()) +     scale_x_discrete(expand = expansion(mult = c(0,0))) +      scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, 1)) +
    scale_fill_manual(values=c("#00CCCC","#009E73"))
ggsave("../Figures/PopPersistence/Fig5_PopPers_ISCtrl_Y3.png", width=10, height=5, units="in")
```

### Italy x Sweden HH
```{r}
#First, make a contingency table from the data
y3humid_contingtable <- table(y3humid$Dormancy, y3humid$Y3Resurrection)

#Perform a chi-square test 
y3humidchisq <- chisq.test(y3humid_contingtable)

#make a graph - convert to long format 
y3humidprop <- prop.table(y3humid_contingtable, 1) #proportions 

humiddfpers <- as.data.frame.matrix(y3humidprop)
humiddfpers$DORM <- c("Dormant", "Mixed", "Non-Dormant")
humiddfpers$RIL <-c("Drought","Drought","Drought")
humiddfpers_long <- gather(humiddfpers, Status, Proportion, "Persisted":"Reappeared", factor_key=TRUE)
  
humidy1persgraph <- humiddfpers_long %>% ggplot(aes(y=Proportion, x=DORM, fill=factor(Status, level=level_order_y3))) + 
    geom_bar(stat="identity", position = "fill", alpha=0.9) + 
    theme_classic() + 
    theme(text=element_text(size=30), legend.position = "none",            axis.title.y=element_blank(), axis.text.y=element_blank(),           axis.title.x=element_blank(), axis.text.x=element_blank()) +     scale_x_discrete(expand = expansion(mult = c(0,0))) +      scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, 1)) +
    scale_fill_manual(values=c("#00CCCC","#009E73"))
ggsave("../Figures/PopPersistence/Fig5_PopPers_ISHH_Y3.png", width=10, height=5, units="in")
```

### Italy x Sweden Native Soil
```{r}
#First, make a contingency table from the data
y3soil_contingtable <- table(y3soil$Dormancy, y3soil$Y3Resurrection)

#Perform a chi-square test 
y3soilchisq <- chisq.test(y3soil_contingtable)

#make a graph - convert to long format 
y3soilprop <- prop.table(y3soil_contingtable, 1) #proportions 

soildfpers <- as.data.frame.matrix(y3soilprop)
soildfpers$DORM <- c("Dormant", "Mixed", "Non-Dormant")
soildfpers$RIL <-c("Drought","Drought","Drought")
soildfpers_long <- gather(soildfpers, Status, Proportion, "Disappeared":"Reappeared", factor_key=TRUE)
  
soily1persgraph <- soildfpers_long %>% ggplot(aes(y=Proportion, x=DORM, fill=factor(Status, level=level_order_y3))) + 
    geom_bar(stat="identity", position = "fill", alpha=0.9) + 
    theme_classic() + 
    theme(text=element_text(size=30), legend.position = "none",            axis.title.y=element_blank(), axis.text.y=element_blank(),           axis.title.x=element_blank(), axis.text.x=element_blank()) +     scale_x_discrete(expand = expansion(mult = c(0,0))) +      scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, 1)) +
    scale_fill_manual(values=c("#FFFF99","#00CCCC","#009E73"))
ggsave("../Figures/PopPersistence/Fig5_PopPers_ISNS_Y3.png", width=10, height=5, units="in")
```

### Italy x Sweden Litter
```{r}
#First, make a contingency table from the data
y3straw_contingtable <- table(y3straw$Dormancy, y3straw$Y3Resurrection)

#Perform a chi-square test 
y3strawchisq <- chisq.test(y3straw_contingtable)

#make a graph - convert to long format 
y3strawprop <- prop.table(y3straw_contingtable, 1) #proportions 

strawdfpers <- as.data.frame.matrix(y3strawprop)
strawdfpers$DORM <- c("Dormant", "Mixed", "Non-Dormant")
strawdfpers$RIL <-c("Drought","Drought","Drought")
strawdfpers_long <- gather(strawdfpers, Status, Proportion, "Persisted":"Reappeared", factor_key=TRUE)
  
strawy1persgraph <- strawdfpers_long %>% ggplot(aes(y=Proportion, x=DORM, fill=factor(Status, level=level_order_y3))) + 
    geom_bar(stat="identity", position = "fill", alpha=0.9) + 
    theme_classic() + 
    theme(text=element_text(size=30), legend.position = "none",            axis.title.y=element_blank(), axis.text.y=element_blank(),           axis.title.x=element_blank(), axis.text.x=element_blank()) +     scale_x_discrete(expand = expansion(mult = c(0,0))) +      scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, 1)) +
    scale_fill_manual(values=c("#00CCCC","#009E73"))
ggsave("../Figures/PopPersistence/Fig5_PopPers_ISLitter_Y3.png", width=10, height=5, units="in")
```