---
title: "ProjectionMatrix"
author: "Brandie QC"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Code for the population projection matrix (Figure 6)

## Load Libraries
```{r}
library(tidyverse)
library(popbio) #https://cran.r-project.org/web/packages/popbio/popbio.pdf 
library(boot)
library(broom)

BQSBPalette <- c("#FF9900","#B266FF", "#00CC00","#999999", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
BQDNDPalette <- c("#FF9900","#00CC00","#B266FF", "#999999", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

Dorm_order <- c("High", "Mixed", "Low")
Envt_order <- c('Control','High Humidity','Native Soil','Litter')

sem <- function(x, na.rm=FALSE) {           #for calculating standard error
  sd(x,na.rm=na.rm)/sqrt(length(na.omit(x)))
} 

set.seed(15)
```

## Load the Data

```{r}
allsbdata <- read_csv("../Raw.Data/AllSBData.csv") #SB pots weekly census data 
allsbdata_pop <- unite(allsbdata, "PopId", c(Col,Row)) #create PopId column 

minsdls_IC_cages <- read_csv("../Processed.Data/TotalSeedlings.csv")

fruits_cages <- read_csv("../Raw.Data/AllYearsRepTraits.csv") %>% #fruit number per individual per pop in cages 
  select(Block:BandColor, Fruits)
fruits_cages_popid <- unite(fruits_cages, "PopId", c(Col,Row))

y1totalseeds <- tibble(RILSet=c("Italy x Sweden", "Italy x Sweden", "Germany x Tajikistan", "Germany x Tajikistan", "UK x USA", "UK x USA", "Italy x Sweden" ,"Germany x Tajikistan","UK x USA"), Dormancy=c("Dormant", "Non-Dormant", "Dormant", "Non-Dormant", "Dormant", "Non-Dormant", "Mixed", "Mixed","Mixed"), TotalSeeds=c(622, 622, 617, 617, 624, 624, 624, 616, 640)) #total number of seeds planted in each pop

allcages_popdata <- read_csv("../Processed.Data/AllYearsPopCensus_PopSize.csv") #weekly census data for pop cages. 
allcages_popdata_id <- unite(allcages_popdata, "PopId", c(Col,Row)) #create PopId column 

censusdates_all <- read_csv("../Raw.Data/CensusDates_All.csv") #to match censsus numbers to dates and years 
censusdates_all <- unite(censusdates_all, "PopId", c(Col,Row))
censusdates_all$Date <- as.Date(censusdates_all$Date, format = "%m/%d/%y")
censusdates_all_julian <- censusdates_all %>% mutate(JulianDate = yday(censusdates_all$Date))

totalrose_IC_cages <- read_csv("../Processed.Data/TotalRosettes.csv") # total number new rose for each pop cage and year

total_FRMD_cages <- read_csv("../Processed.Data/TotalRep.csv") # total number new rep for each pop cage and year
```

## Need estimate of number of seeds planted inside the circle
### Get proportion of rosettes inside circle out of total rosettes in each pop cage 
```{r}
#calculate total rosettes outside circle
rosettes_OC_long <- allcages_popdata_id %>% filter(Year != 3) %>% #not enough rosette data in year 3 
  select(Block:Ident, CensusN, RosetteN.OC) 
rosettes_OC_wide = spread(rosettes_OC_long, CensusN, RosetteN.OC)
rosettes_OC_wide_new <- rosettes_OC_wide
rosettes_OC_wide_new[10:54] = rosettes_OC_wide_new[10:54] - rosettes_OC_wide_new[(10:54)-1] #calculate the number of new rosettes at each census

#convert back to long
newrosettes_OC_long = gather(rosettes_OC_wide_new, CensusN, Newrosettes, "1.01":"2.21", factor_key = TRUE)

#convert negatives into 0s
newrosettes_OC_long$Newrosettes <- ifelse(newrosettes_OC_long$Newrosettes < 0, 0, newrosettes_OC_long$Newrosettes)

#add in date info
newrosettes_OC_long$CensusN <- as.character(newrosettes_OC_long$CensusN)
newrosettes_OC_long_dates <- merge(newrosettes_OC_long, censusdates_all_julian)
totalrosettes_OC <- newrosettes_OC_long_dates %>% group_by(PopId, Block, RILSet, Dormancy, Envt, Year) %>% 
  filter(!is.na(Newrosettes)) %>% 
  summarize(OCTotalrosettes=sum(Newrosettes))

totalrosettes_circle <- totalrose_IC_cages %>% rename(CircleTotalrosettes=Totalrosettes)

#proportion of rosettes in each pop that were in circle vs. OC
rose_wholepop <- left_join(totalrosettes_OC, totalrosettes_circle) %>%
  mutate(COCTOTROSE=CircleTotalrosettes+OCTotalrosettes, 
         PropCircleRose=CircleTotalrosettes/COCTOTROSE)
```

### Calculating total seeds planted in circle
```{r}
#for pops with no surv to rose in year 1, use the averages per environmental treatment 
propcirclerose_summary <- rose_wholepop %>% 
  filter(RILSet=="Italy x Sweden", Year == 1) %>% 
  filter(!is.na(PropCircleRose)) %>% 
  group_by(Envt, Year) %>% 
  summarise(meanProp=mean(PropCircleRose), SE=sd(PropCircleRose)/sqrt(n()))

y1totalseeds_IC_cages_wrose <- left_join(rose_wholepop, y1totalseeds) %>% 
  filter(RILSet=="Italy x Sweden", Year == 1) %>% 
  filter(!is.na(PropCircleRose)) %>% #for pops with rosettes
  mutate(CircleSeeds = ifelse(PropCircleRose==0, 0.1*TotalSeeds, #assume that at least some seeds made it in the circle
                            ifelse(PropCircleRose==1, 0.9*TotalSeeds, #assume that at least some seeds made it outside the circle 
                                   TotalSeeds*PropCircleRose))) %>% 
  select(PopId:Year, PropCircleRose:CircleSeeds)

y1totalseeds_IC_cages_norose <- left_join(rose_wholepop, y1totalseeds) %>% 
  filter(RILSet=="Italy x Sweden", Year == 1) %>% 
  filter(is.na(PropCircleRose)) %>% #for pops w/ no rose 
  mutate(CircleSeeds=ifelse(Envt=="Control", 0.74*TotalSeeds,
                            ifelse(Envt=="High Humidity", 0.81*TotalSeeds,
                                   ifelse(Envt=="Litter", 0.68*TotalSeeds,
                                          0.99*TotalSeeds)))) %>% 
  select(PopId:Year, PropCircleRose:CircleSeeds)

y1totalseeds_IC_cages <- rbind(y1totalseeds_IC_cages_wrose, y1totalseeds_IC_cages_norose)
nrow(y1totalseeds_IC_cages) #96 rows for all 96 Italy x Sweden pops
```

## Investigating Early Rep Pops
```{r}
allcages_popdata_id %>% filter(CensusN <=1.19) %>%
   mutate(TotalRep = Fruiting.circle+mat.dead.circle+Fruiting.OC+mat.dead.OC) %>% 
  group_by(PopId) %>% 
  summarise(sumTotalRep=sum(TotalRep, na.rm = TRUE)) %>% #this is not a real sum of rep (just a way for me to see which pops had some summer/early fall rep)
  filter(sumTotalRep >0)

#12 pops with summer/early fall rep 
#A3 (litter), A4 (humidity, mixed), A5 (litter), B2 (HH, ND), B4 (HH, D), B6 (HH, ND), B13 (litter), C3 (litter), C4 (BS,litter), C7 (control, D), L5 (BS, litter), M10 (BS, litter)

#label those populations so I can remove them from the germ calcs
early_rep <- allcages_popdata_id %>% 
   filter(CensusN <=1.19) %>%
   mutate(TotalRep = Fruiting.circle+mat.dead.circle+Fruiting.OC+mat.dead.OC) %>% 
   group_by(PopId) %>% 
   summarise(sumTotalRep=sum(TotalRep, na.rm = TRUE)) %>%  #this is not a real sum of rep (just a way for me to see which pops had some summer/early fall rep)
  mutate(Early.Rep=if_else(sumTotalRep==0, "no", "yes")) %>% 
  select(PopId, Early.Rep)
```

Merge with germ data
```{r}
minsdls_IC_cages_early_rep <- left_join(minsdls_IC_cages, early_rep)
```

## Vital Rates

### Year 1 Fresh Seeds Germination Rate (G.f)

-   min fresh from cages = \# of min sdls in circle in year 1 / \# of seeds planted in circle in year 1

```{r}
y1_mingerms <- minsdls_IC_cages_early_rep %>%
  filter(RILSet=="Italy x Sweden", Early.Rep == "no") %>% 
  filter(Year == 1) %>% 
  select(PopId:Envt, Y1Germs=Totalsdls)

y1_minfreshgerm <- left_join(y1totalseeds_IC_cages, y1_mingerms) %>% 
  mutate(MinFreshGermProp = Y1Germs/CircleSeeds) %>% 
  select(PopId:Block, Dormancy:Envt, CircleSeeds:MinFreshGermProp)

y1_minfreshgerm %>% filter(MinFreshGermProp >= 1) #0 cases where more germs than seeds planted 
```

## Germination Rate of Seeds in the Seedbank (Gsb)

-   seed bank germination from SB pots = \# of germs in year 2 of SB pots / (\# of seeds planted - \# of germs in year 1 of SB pots)

```{r}
allsbdatatotal_year <- allsbdata_pop %>% group_by(PopId, Block, Dormancy, EnvtTrt, Year) %>% 
  summarise(ConfTotal = sum(Confirmed.Total, na.rm = TRUE), MaxTotal = sum(Max.Total, na.rm = TRUE)) #total germination for each pop and year 

sbseeds_sbpots <- allsbdatatotal_year %>% filter(Year==1) %>% 
  mutate(SBSeeds_Max = 114-MaxTotal, SBSeeds_Min = 114-ConfTotal) %>% select(PopId:EnvtTrt, SBSeeds_Max, SBSeeds_Min)

y2germs_sbpots <- allsbdatatotal_year %>% filter(Year == 2) %>% 
  select(PopId:EnvtTrt, MaxTotal, ConfTotal)

sbg_sbspots <- left_join(y2germs_sbpots, sbseeds_sbpots) %>% 
  mutate(GermProp_Max=MaxTotal/SBSeeds_Max, GermProp_Min=ConfTotal/SBSeeds_Min)
```

### Maximum sbg across all cages and pots 
```{r}
#from individual pops
summary(sbg_sbspots) #Max: 0.151515   Conf: 0.131579

#from trt avgs 
sbg_sbspots_summary <- sbg_sbspots %>% 
  group_by(Dormancy, EnvtTrt) %>% 
  summarise(meanGermProp_Conf=mean(GermProp_Min, na.rm = TRUE), semConf=sem(GermProp_Min),
            meanGermProp_Max=mean(GermProp_Max), semMax=sem(GermProp_Max))
summary(sbg_sbspots_summary) # Max.   :0.037035 and  Min   :0.030583 

##Use 0.1516
```

## Survival of seeds in seedbank (for 1 year)
```{r}
allsbdatatotal <- allsbdata_pop %>% group_by(PopId, Block, Dormancy, EnvtTrt) %>% 
  summarise(ConfTotal = sum(Confirmed.Total, na.rm = TRUE), MaxTotal = sum(Max.Total, na.rm = TRUE)) #total germination for each pop across both years 

seed_surv <- allsbdatatotal %>% mutate(ConfSdlSurv=ConfTotal/114, MaxSdlSurv=MaxTotal/114) #assume that any seeds that did not germinate died 

seed_surv_summary <- seed_surv %>% group_by(Dormancy, EnvtTrt) %>% summarise(meanConfSdlSurv=mean(ConfSdlSurv), SEC=sd(ConfSdlSurv)/sqrt(n()), meanMaxSdlSurv=mean(MaxSdlSurv), SEM=sd(MaxSdlSurv)/sqrt(n()))

seed_surv_summary %>% ggplot(aes(x=EnvtTrt, y=meanMaxSdlSurv, group=Dormancy, fill=Dormancy)) +
    geom_col(width = 0.7,position = position_dodge(0.75)) +
    geom_errorbar(aes(ymin=meanMaxSdlSurv-SEM,ymax=meanMaxSdlSurv+SEM),width=.2, position = 
                    position_dodge(0.75)) +
    theme_classic() +
    xlab("Environmental Treatment") +
   ylab("Proportion of Seed Survival") +
   scale_fill_manual(values=BQSBPalette) +
   # theme(text=element_text(size=37)) +
   ggtitle("Max Total") +
    scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(0, 1)) 
```

### Note: no seed survival for the Litter treatment - get the average for dorm/non-dorm
```{r}
seed_surv_summary_allenv <- seed_surv %>% group_by(Dormancy) %>% summarise(meanConfSdlSurv=mean(ConfSdlSurv), SEC=sd(ConfSdlSurv)/sqrt(n()), meanMaxSdlSurv=mean(MaxSdlSurv), SEM=sd(MaxSdlSurv)/sqrt(n()))

seed_surv_summary_allenv %>% ggplot(aes(x=Dormancy, y=meanConfSdlSurv)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
    geom_errorbar(aes(ymin=meanConfSdlSurv-SEC,ymax=meanConfSdlSurv+SEC),width=.2, position = 
                    position_dodge(0.75)) +
    theme_classic() 

seed_surv_summary_allenv %>% ggplot(aes(x=Dormancy, y=meanMaxSdlSurv)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
    geom_errorbar(aes(ymin=meanMaxSdlSurv-SEM,ymax=meanMaxSdlSurv+SEM),width=.2, position = 
                    position_dodge(0.75)) +
    theme_classic() 
```

### Note: no seed survival for the Mixed treatment - so take mean of envts
```{r}
seed_surv_mixed_summary <-  seed_surv %>%
  group_by(EnvtTrt) %>% 
  summarise(meanConfSdlSurv=mean(ConfSdlSurv), SEC=sd(ConfSdlSurv)/sqrt(n()), meanMaxSdlSurv=mean(MaxSdlSurv), SEM=sd(MaxSdlSurv)/sqrt(n()))
```

## Survival to Reproduction (Srep)
```{r}
#from max germ 
minsdls_IC_cages_noy3 <- minsdls_IC_cages %>% 
  filter(Year!=3) %>% 
  select(PopId:Year, Totalsdls)

survtoFRMDfromsdl_circle_min <- full_join(total_FRMD_cages, minsdls_IC_cages_noy3) %>% 
  filter(RILSet=="Italy x Sweden") %>% 
  select(PopId:Year, TotalFRMD, Totalsdls) %>% 
  mutate(SurvtoRep = ifelse(Totalsdls==0, 0, TotalFRMD/Totalsdls))
```

## Fecundity (F)
```{r}
#avg rep = each indiv fruit number *29 averaged for each pop
fruits_to_seeds <- fruits_cages_popid %>% 
  filter(RILSet=="IS") %>% 
  mutate(EstSeeds=Fruits*29) %>% 
  group_by(PopId, Block, Dormancy, Envt, Year) %>% 
  summarise(meanEstSeeds=mean(EstSeeds)) %>% 
  select(PopId:Year, meanEstSeeds)
#fruits_to_seeds %>% arrange(Block, Envt, Dormancy)
#only counted fruit for 5 blocks! - 60 populations 

fecundity <- left_join(total_FRMD_cages, fruits_to_seeds) %>% 
  filter(RILSet=="Italy x Sweden") %>% 
  filter(Block!=1, Block!=5, Block!=6) %>%  #Blocks 2, 3, 4, 7, 8 were consistently measured
  mutate(meanEstSeeds=if_else(TotalFRMD == 0, 0, meanEstSeeds)) %>%  #fill in 0 estimated seeds when there were 0 rep indivs 
  select(PopId:Year, TotalFRMD, meanEstSeeds)
dim(fecundity) #60 pops
fecundity %>% filter(is.na(meanEstSeeds)) #3 populations with some surv to rep inside the circle but no fecundity estimate 
##Notes say J4 was skipped because all plants had decomposed before the fruit counts - L3 likely skipped for the same reason 
##unknown why no data for the 1 rep indiv in F8 in year 2 
```

## Make a data sheet that has all the vital rates in it for each population

### Merge 
```{r}
#gf.min.cages, gsb.0, gsb.max, srep.good, srep.bad, F.good, F.bad
#gsb.max=0.1516 

fecundity_mergeprep <- fecundity %>% 
  select(PopId:Envt, Year, meanEstSeeds) %>% 
  pivot_wider(names_from = Year, values_from = meanEstSeeds) %>% 
  rename(F.good = "1", F.bad="2")
#fecundity_mergeprep

survtoFRMDfromsdl_circle_min_mergeprep <- survtoFRMDfromsdl_circle_min %>% 
  select(PopId:Envt, Year, SurvtoRep) %>% 
  pivot_wider(names_from = Year, values_from = SurvtoRep) %>% 
   rename(srep.good = "1", srep.bad="2")
#survtoFRMDfromsdl_circle_max_mergeprep

w_merge <- left_join(fecundity_mergeprep, survtoFRMDfromsdl_circle_min_mergeprep)
#w_merge

germ_merge_prep <- y1_minfreshgerm %>% 
  select(RILSet:Envt, MinFreshGermProp) %>% 
  rename(gf.min.cages=MinFreshGermProp) %>% 
  mutate(gsb.0=0, gsb.max=0.1516)
#germ_merge_prep

all_vital_merge <- left_join(w_merge, germ_merge_prep) %>% 
  select(PopId:Envt, gf.min.cages, gsb.0, gsb.max, srep.good, srep.bad, F.good, F.bad)
#all_vital_merge

all_vital_merge %>% filter(is.na(gf.min.cages)) #all 0s at remaining life stages except pop B_6
#B_6 removed from germ calcs because it had summer rep
```

### Add Seed survival 
```{r}
seed_surv_summary_prep <- seed_surv_summary %>% 
  select(Dormancy, Envt=EnvtTrt, Sseed.max=meanMaxSdlSurv)

seed_surv_summary_allenv_prep <- seed_surv_summary_allenv %>% 
  mutate(Envt="Litter") %>% 
  select(Dormancy, Envt, Sseed.max=meanMaxSdlSurv)

seed_surv_mixed_summary_prep <- seed_surv_mixed_summary %>% 
  mutate(Dormancy="Mixed") %>% 
  select(Dormancy, Envt=EnvtTrt, Sseed.max=meanMaxSdlSurv)
summary(seed_surv_mixed_summary_prep)

summary(seed_surv)
seed_surv_mixed_litter <- tibble(Dormancy="Mixed", Envt="Litter", Sseed.max=0.24232) #overall mean Sseed since I don't have any other way of estimating this 

seed_surv_merge_prep <- bind_rows(seed_surv_summary_prep, seed_surv_summary_allenv_prep, seed_surv_mixed_summary_prep, seed_surv_mixed_litter) 
seed_surv_merge_prep

all_vital_merge_sseed <- left_join(all_vital_merge, seed_surv_merge_prep) %>% 
  unite("DormEnvt", c(Dormancy, Envt), remove = FALSE)
all_vital_merge_sseed

trts_g.a.min <- all_vital_merge_sseed %>% select(DormEnvt) %>% 
  arrange(DormEnvt) %>% unique() %>% pull(DormEnvt)
trts_g.a.min
```

## Bootstrapping
Randomly sample which pops go into the avg calcs, then use that "bootstrapped avg" to calculate the matrix elements to get confidence intervals around lambda

### Make a nested data frame with one row for each block.
Boot will sample each block with replacement 
```{r}
all_vital_boot_nest <- all_vital_merge_sseed %>% 
  nest(.by=Block)
```

### Create the lambda_calc function 
```{r}
DNDPM.1 = matrix (0, 2, 2)
DNDPM.2 = matrix (0, 2, 2)
DNDPM.3 = matrix (0, 2, 2)
DNDPM.4 = matrix (0, 2, 2)

LAVALUES_boot = matrix(0, 12, 4) #12 rows for the treatments, 4 columns for the models
rownames(LAVALUES_boot) <- trts_g.a.min
#LAVALUES_boot

lambda_calc <- function(data, indices) {
  #data has to be nested by block 
  
  data <- data[indices,] #subset per bootstrap indices
  
  data <- data %>% unnest(data) #unnest so the function can access the vital rates
  
  data_means <- data %>% 
    group_by(Dormancy, Envt) %>% 
  summarise(mean_gf.min.cages = mean(gf.min.cages, na.rm = TRUE), 
            mean_gsb.0 = mean(gsb.0), 
            mean_gsb.max = mean(gsb.max), 
            mean_Sseed.max = mean(Sseed.max),
            mean_srep.good = mean(srep.good), 
            mean_srep.bad = mean(srep.bad), 
            mean_F.good = mean(F.good, na.rm = TRUE), 
            mean_F.bad = mean(F.bad, na.rm = TRUE)) %>% 
  unite("DormEnvt", c(Dormancy, Envt), remove = FALSE)

for (i in trts_g.a.min) {
  vtal_sub <- data_means %>% filter(DormEnvt==i)
  DNDPM.1[1,1] = (vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good) + ((1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max*vtal_sub$mean_gsb.0*vtal_sub$mean_srep.good*vtal_sub$mean_F.good)
  DNDPM.1[1,2] = vtal_sub$mean_gsb.0*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good
  DNDPM.1[2,1] = vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  DNDPM.1[2,2] = vtal_sub$mean_gsb.0*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  
  DNDPM.2[1,1] = (vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good) + ((1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max*vtal_sub$mean_gsb.max*vtal_sub$mean_srep.good*vtal_sub$mean_F.good)
  DNDPM.2[1,2] = vtal_sub$mean_gsb.max*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good
  DNDPM.2[2,1] = vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  DNDPM.2[2,2] = vtal_sub$mean_gsb.max*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  
  DNDPM.3[1,1] = (vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.bad*vtal_sub$mean_F.bad) + ((1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max*vtal_sub$mean_gsb.0*vtal_sub$mean_srep.bad*vtal_sub$mean_F.bad)
  DNDPM.3[1,2] = vtal_sub$mean_gsb.0*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.bad*vtal_sub$mean_F.bad
  DNDPM.3[2,1] = vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  DNDPM.3[2,2] = vtal_sub$mean_gsb.0*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  
  DNDPM.4[1,1] = (vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.bad*vtal_sub$mean_F.bad) + ((1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max*vtal_sub$mean_gsb.max*vtal_sub$mean_srep.bad*vtal_sub$mean_F.bad)
  DNDPM.4[1,2] = vtal_sub$mean_gsb.max*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.bad*vtal_sub$mean_F.bad
  DNDPM.4[2,1] = vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  DNDPM.4[2,2] = vtal_sub$mean_gsb.max*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  
  if (is.na(DNDPM.1[1,1]))  {
   LAVALUES_boot[i,1]= NA 
  }
  
  if (!is.na(DNDPM.1[1,1])) {
 LAVALUES_boot[i,1]= lambda(DNDPM.1) 
  }
  
  if (is.na(DNDPM.2[1,1]))  {
   LAVALUES_boot[i,2]= NA 
  }
  
  if (!is.na(DNDPM.2[1,1])) {
 LAVALUES_boot[i,2]= lambda(DNDPM.2) 
  }
  
  if (is.na(DNDPM.3[1,1]))  {
   LAVALUES_boot[i,3]= NA 
  }
  
  if (!is.na(DNDPM.3[1,1])) {
 LAVALUES_boot[i,3]= lambda(DNDPM.3) 
  }
  
if (is.na(DNDPM.4[1,1]))  {
   LAVALUES_boot[i,4]= NA 
  }
  
  if (!is.na(DNDPM.4[1,1])) {
 LAVALUES_boot[i,4]= lambda(DNDPM.4) 
  }
}
  LAVALUES_boot
}

#lambda_calc(all_vital_boot_nest) #function works 
```

Log Transformed Lambda
```{r}
LAVALUES_boot_log = matrix(0, 12, 4) #12 rows for the treatments, 4 columns for the models
rownames(LAVALUES_boot_log) <- trts_g.a.min
#LAVALUES_boot

lambda_calc_log <- function(data, indices) {
  #data has to be nested by block 
  
  data <- data[indices,] #subset per bootstrap indices
  
  data <- data %>% unnest(data) #unnest so the function can access the vital rates
  
  data_means <- data %>% 
    group_by(Dormancy, Envt) %>% 
  summarise(mean_gf.min.cages = mean(gf.min.cages, na.rm = TRUE), 
            mean_gsb.0 = mean(gsb.0), 
            mean_gsb.max = mean(gsb.max), 
            mean_Sseed.max = mean(Sseed.max),
            mean_srep.good = mean(srep.good), 
            mean_srep.bad = mean(srep.bad), 
            mean_F.good = mean(F.good, na.rm = TRUE), 
            mean_F.bad = mean(F.bad, na.rm = TRUE)) %>% 
  unite("DormEnvt", c(Dormancy, Envt), remove = FALSE)

for (i in trts_g.a.min) {
  vtal_sub <- data_means %>% filter(DormEnvt==i)
  DNDPM.1[1,1] = (vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good) + ((1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max*vtal_sub$mean_gsb.0*vtal_sub$mean_srep.good*vtal_sub$mean_F.good)
  DNDPM.1[1,2] = vtal_sub$mean_gsb.0*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good
  DNDPM.1[2,1] = vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  DNDPM.1[2,2] = vtal_sub$mean_gsb.0*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  
  DNDPM.2[1,1] = (vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good) + ((1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max*vtal_sub$mean_gsb.max*vtal_sub$mean_srep.good*vtal_sub$mean_F.good)
  DNDPM.2[1,2] = vtal_sub$mean_gsb.max*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good
  DNDPM.2[2,1] = vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  DNDPM.2[2,2] = vtal_sub$mean_gsb.max*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  
  DNDPM.3[1,1] = (vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.bad*vtal_sub$mean_F.bad) + ((1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max*vtal_sub$mean_gsb.0*vtal_sub$mean_srep.bad*vtal_sub$mean_F.bad)
  DNDPM.3[1,2] = vtal_sub$mean_gsb.0*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.bad*vtal_sub$mean_F.bad
  DNDPM.3[2,1] = vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  DNDPM.3[2,2] = vtal_sub$mean_gsb.0*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  
  DNDPM.4[1,1] = (vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.bad*vtal_sub$mean_F.bad) + ((1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max*vtal_sub$mean_gsb.max*vtal_sub$mean_srep.bad*vtal_sub$mean_F.bad)
  DNDPM.4[1,2] = vtal_sub$mean_gsb.max*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.bad*vtal_sub$mean_F.bad
  DNDPM.4[2,1] = vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  DNDPM.4[2,2] = vtal_sub$mean_gsb.max*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  
  if (is.na(DNDPM.1[1,1]))  {
   LAVALUES_boot_log[i,1]= NA 
  }
  
  if (!is.na(DNDPM.1[1,1])) {
 LAVALUES_boot_log[i,1]= log(lambda(DNDPM.1)+1) 
  }
  
  if (is.na(DNDPM.2[1,1]))  {
   LAVALUES_boot_log[i,2]= NA 
  }
  
  if (!is.na(DNDPM.2[1,1])) {
 LAVALUES_boot_log[i,2]= log(lambda(DNDPM.2)+1) 
  }
  
  if (is.na(DNDPM.3[1,1]))  {
   LAVALUES_boot_log[i,3]= NA 
  }
  
  if (!is.na(DNDPM.3[1,1])) {
 LAVALUES_boot_log[i,3]= log(lambda(DNDPM.3)+1) 
  }
  
if (is.na(DNDPM.4[1,1]))  {
   LAVALUES_boot_log[i,4]= NA 
  }
  
  if (!is.na(DNDPM.4[1,1])) {
 LAVALUES_boot_log[i,4]= log(lambda(DNDPM.4)+1) 
  }
}
  LAVALUES_boot_log
}
```

### Perform the bootstrap sampling
```{r}
lambda.boot <- boot(data=all_vital_boot_nest, statistic = lambda_calc, R=1000)

#str(lambda.boot)
lambda.boot$t0 #looks correct

for(i in 1:2) {
  plot(lambda.boot, index=i) #distributions look pretty skewed 
}

#boot.ci(lambda.boot, type = "basic", index = 1)
boot_results <- tidy(lambda.boot,conf.int=TRUE,conf.method="basic") 
boot_results_perc <- tidy(lambda.boot,conf.int=TRUE,conf.method="perc") 

trt_model_info <- as_tibble(trts_g.a.min) %>% 
  rename(Treatment=value) %>% 
  group_by(Treatment) %>% 
  expand(Model = seq(1:4)) %>% 
  arrange(Model) %>% 
  separate(Treatment, into = c("Dormancy","Envt"), 
           sep = "_", remove = FALSE)

boot_results_trts <- bind_cols(trt_model_info, boot_results) %>% 
  rename(Lambda=statistic)
boot_results_trts
write.csv(boot_results_trts, "../Processed.Data/BootLambdas.csv", row.names = FALSE)

boot_results_trts_perc <- bind_cols(trt_model_info, boot_results_perc) %>% 
  rename(Lambda=statistic)
```

### Log Transformed Lambda Bootstrap Sampling
```{r}
lambda.boot_log <- boot(data=all_vital_boot_nest, statistic = lambda_calc_log, R=1000)

boot_results_perc_log <- tidy(lambda.boot_log,conf.int=TRUE,conf.method="perc") 

boot_results_log_trts_perc <- bind_cols(trt_model_info, boot_results_perc_log) %>% 
  rename(logLambda=statistic) %>% 
  mutate(Dormancy=str_replace(Dormancy, "Non-Dormant", "Low")) %>% 
  mutate(Dormancy=str_replace(Dormancy, "Dormant", "High"))
```

### View bootstrap results
Log transformed lambda 
```{r}
model_names <- as_labeller(
  c("1"="Model 1: \n No SB, 2 Good Years",
    "2"="Model 2: \n Max SB, 2 Good years",
    "3"="Model 3: \n No SB, 1 Good & 1 Bad Year",
    "4"="Model 4: \n Max SB, 1 Good & 1 Bad Year"))

boot_results_log_trts_perc$Envt <- factor(boot_results_log_trts_perc$Envt, levels = Envt_order)
boot_results_log_trts_perc$Dormancy <- factor(boot_results_log_trts_perc$Dormancy, levels = Dorm_order)

boot_fig_perc_log <- boot_results_log_trts_perc %>% 
  ggplot(aes(x=Envt, y=logLambda, group = Dormancy, fill = Dormancy)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
    geom_errorbar(aes(ymin=conf.low,ymax=conf.high),
                  width=.1, position = 
                    position_dodge(0.75)) +
    theme_classic() +
    xlab("Environmental Treatment") +
    ylab(paste0("log(Asymptotic Lambda)")) +
    scale_fill_manual(values=BQDNDPalette) +
  theme(text=element_text(size=25), axis.text.x = element_text(angle = 45,  hjust = 1)) +
  annotate("segment", x = 0, xend = 4.5, y = 0.6931472, yend = 0.6931472, colour = "blue", linetype=2) +
  facet_wrap(~Model, scales = "free", labeller = model_names)
ggsave("../Figures/Fig6_Boot_AsympLambda_Perc_Log.png", width=13, height=10, units="in")
```

## Calculate Sensitivities  

### Treatment means
```{r}
all_vital_trtmeans <- all_vital_merge_sseed %>% 
  group_by(Dormancy, Envt) %>% 
  summarise(mean_gf.min.cages = mean(gf.min.cages, na.rm = TRUE), 
            mean_gsb.0 = mean(gsb.0), 
            mean_gsb.max = mean(gsb.max), 
            mean_Sseed.max = mean(Sseed.max),
            mean_srep.good = mean(srep.good), 
            mean_srep.bad = mean(srep.bad), 
            mean_F.good = mean(F.good, na.rm = TRUE), 
            mean_F.bad = mean(F.bad, na.rm = TRUE)) %>% 
  unite("DormEnvt", c(Dormancy, Envt), remove = FALSE)
```

### For loop for getting sensitivities 
```{r}
for (i in trts_g.a.min) {
  vtal_sub <- all_vital_trtmeans %>% filter(DormEnvt==i)
  DNDPM.1[1,1] = (vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good) + ((1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max*vtal_sub$mean_gsb.0*vtal_sub$mean_srep.good*vtal_sub$mean_F.good)
  DNDPM.1[1,2] = vtal_sub$mean_gsb.0*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good
  DNDPM.1[2,1] = vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  DNDPM.1[2,2] = vtal_sub$mean_gsb.0*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  
  print(sensitivity(DNDPM.1))
  print(lambda(DNDPM.1))
  
  DNDPM.2[1,1] = (vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good) + ((1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max*vtal_sub$mean_gsb.max*vtal_sub$mean_srep.good*vtal_sub$mean_F.good)
  DNDPM.2[1,2] = vtal_sub$mean_gsb.max*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good
  DNDPM.2[2,1] = vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  DNDPM.2[2,2] = vtal_sub$mean_gsb.max*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  
  print(sensitivity(DNDPM.2))
  print(lambda(DNDPM.2))
  
  DNDPM.3[1,1] = (vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.bad*vtal_sub$mean_F.bad) + ((1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max*vtal_sub$mean_gsb.0*vtal_sub$mean_srep.bad*vtal_sub$mean_F.bad)
  DNDPM.3[1,2] = vtal_sub$mean_gsb.0*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.bad*vtal_sub$mean_F.bad
  DNDPM.3[2,1] = vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  DNDPM.3[2,2] = vtal_sub$mean_gsb.0*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  
  print(sensitivity(DNDPM.3))
  print(lambda(DNDPM.3))
  
  DNDPM.4[1,1] = (vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.bad*vtal_sub$mean_F.bad) + ((1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max*vtal_sub$mean_gsb.max*vtal_sub$mean_srep.bad*vtal_sub$mean_F.bad)
  DNDPM.4[1,2] = vtal_sub$mean_gsb.max*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.bad*vtal_sub$mean_F.bad
  DNDPM.4[2,1] = vtal_sub$mean_gf.min.cages*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max
  DNDPM.4[2,2] = vtal_sub$mean_gsb.max*vtal_sub$mean_srep.good*vtal_sub$mean_F.good*(1-vtal_sub$mean_gf.min.cages)*vtal_sub$mean_Sseed.max

  print(sensitivity(DNDPM.4))
  print(lambda(DNDPM.4))
}

#output is in the order of trts_g.a.min and model type 
#Ex: First four outputs = Dormant_Control, model 1-4
trts_g.a.min
```
